Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-03-17 analysis/paper/paper.Rmd
Edits to m&m section
Clean up N rate description for 2016 and clarify analysis statement

Subplot N rates were changed from the 2015 rates to use 60 kg/ha split into two applications (control) and 180 kg/ha in three splits.

@@

Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area] and analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].

>>>>

Subplot N rates differed from the 2015 rates. The control was applied as 60 kg/ha split into two applications and a second treatment of 180 kg/ha in three splits was applied.

@@

Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area]. As most of the data did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
